My Publication Title --- Single Author

### 2025-06-26 paper/quarto_aaai/paper.tex
template seems to be working
can't get full width table to work

% REMOVE THIS: bibentry
% This is only needed to show inline citations in the guidelines document. You should not need it and can safely delete it.
\usepackage{bibentry}
% END REMOVE bibentry
\usepackage{amsmath}

@@

\begin{equation}\phantomsection\label{eq-obj}{
\begin{split}
\min_\theta \text{yloss}(\mathbf{M}_\theta(\mathbf{x}),\mathbf{y}) + \lambda_{\text{div}} \text{div}(\mathbf{x}^+,\mathbf{x}_T^\prime,y;\theta) &+ \lambda_{\text{adv}} \text{advloss}(\mathbf{M}_\theta(\mathbf{x}_{t\leq T}^\prime),\mathbf{y}) \\ &+ \lambda_{\text{reg}}\text{ridge}(\mathbf{x}^+,\mathbf{x}_T^\prime,y;\theta)
\end{split}
}\end{equation} where \(\text{yloss}(\cdot)\) is a classification loss
that induces discriminative performance (e.g., cross-entropy). The
second and third terms are explained in detail below. For now, they can
be summarized as inducing explainability directly and indirectly by
penalizing: (1) the contrastive divergence, \(\text{div}(\cdot)\),
between mature counterfactuals \(\mathbf{x}_T^\prime\) and observed
samples \(\mathbf{x}^+\in\mathcal{X}^+=\{\mathbf{x}:y=y^+\}\) in the
target class \(y^+\), and, (2) the adversarial loss,
\(\text{advloss}(.)\), with respect to nascent counterfactuals
\(\mathbf{x}_{t\leq T}^\prime\). Finally, \(\text{ridge}(\cdot)\)
denotes a Ridge penalty (\(\ell_2\)-norm) that regularizes the magnitude
of the energy terms involved in \(\text{div}(\cdot)\)
\citep{du2019implicit}. The trade-off between the components can
governed through penalties \(\lambda_{\text{div}}\),
\(\lambda_{\text{adv}}\) and \(\lambda_{\text{reg}}\).

@@

\begin{figure}

@@

\end{figure}%

@@

To conclude, state-of-the-art machine learning models are prone to
learning complex representations that cannot be interpreted by humans
and existing post-hoc explainability approaches cannot guarantee that
the explanations agree with the model's learned representation of data.
As a step towards addressing this challenge, we introduced
counterfactual training, a novel training regime that incentivizes
highly-explainable models. Our approach leads to explanations that are
both plausible---compliant with the underlying data-generating
process---and actionable---compliant with user-specified mutability
constraints---and thus meaningful to their recipients. Through extensive
experiments we demonstrate that CT satisfies its objective while
promoting robustness and preserving the predictive performance of the
models. It can also be used to fine-tune conventionally-trained models
and achieve similar gains. Finally, this work showcases that it is
practical to improve models \emph{and} their explanations at the same
time.
\end{document}

>>>>

% REMOVE THIS: bibentry
% This is only needed to show inline citations in the guidelines document. You should not need it and can safely delete it.
\usepackage{bibentry}
% END REMOVE bibentry
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

@@

\begin{equation}\phantomsection\label{eq-obj}{
\begin{split}
\min_\theta \text{yloss}(\mathbf{M}_\theta(\mathbf{x}),\mathbf{y}) &+ \lambda_{\text{div}} \text{div}(\mathbf{x}^+,\mathbf{x}_T^\prime,y;\theta) \\+ \lambda_{\text{adv}} \text{advloss}(\mathbf{M}_\theta(\mathbf{x}_{t\leq T}^\prime),\mathbf{y}) &+ \lambda_{\text{reg}}\text{ridge}(\mathbf{x}^+,\mathbf{x}_T^\prime,y;\theta)
\end{split}
}\end{equation} where \(\text{yloss}(\cdot)\) is a classification loss
that induces discriminative performance (e.g., cross-entropy). The
second and third terms are explained in detail below. For now, they can
be summarized as inducing explainability directly and indirectly by
penalizing: (1) the contrastive divergence, \(\text{div}(\cdot)\),
between mature counterfactuals \(\mathbf{x}_T^\prime\) and observed
samples \(\mathbf{x}^+\in\mathcal{X}^+=\{\mathbf{x}:y=y^+\}\) in the
target class \(y^+\), and, (2) the adversarial loss,
\(\text{advloss}(.)\), with respect to nascent counterfactuals
\(\mathbf{x}_{t\leq T}^\prime\). Finally, \(\text{ridge}(\cdot)\)
denotes a Ridge penalty (\(\ell_2\)-norm) that regularizes the magnitude
of the energy terms involved in \(\text{div}(\cdot)\)
\citep{du2019implicit}. The trade-off between the components can
governed through penalties \(\lambda_{\text{div}}\),
\(\lambda_{\text{adv}}\) and \(\lambda_{\text{reg}}\).

@@

\begin{figure*}

@@

\end{figure*}%

@@

To conclude, state-of-the-art machine learning models are prone to
learning complex representations that cannot be interpreted by humans
and existing post-hoc explainability approaches cannot guarantee that
the explanations agree with the model's learned representation of data.
As a step towards addressing this challenge, we introduced
counterfactual training, a novel training regime that incentivizes
highly-explainable models. Our approach leads to explanations that are
both plausible---compliant with the underlying data-generating
process---and actionable---compliant with user-specified mutability
constraints---and thus meaningful to their recipients. Through extensive
experiments we demonstrate that CT satisfies its objective while
promoting robustness and preserving the predictive performance of the
models. It can also be used to fine-tune conventionally-trained models
and achieve similar gains. Finally, this work showcases that it is
practical to improve models \emph{and} their explanations at the same
time.

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\renewcommand{\bibsection}{}
\bibliography{../quarto_ecml/bibliography.bib}
\end{document}
